A brief study of Approximation Algorithms for 2D Packing Problem

### 2021-12-10 paper.tex
writing theorem

\section{Steinberg's Algorithm}
\par In this section we introduce a more advanced approximation algorithm designed by \cite{steinberg1997strip}. Instead of heuristically packing every rectangle and output the height as result, Steinberg gave a more specific bound on the height $\hat{h}$ of the bin, with which a valid packing can be found easily. This is guaranteed by the following theorem.
\paragraph{Steinberg's Theorem} If the following inequalities hold
\begin{eqnarray}
	a_M &= \max_{1\leq i\leq n} a_i \\
	b_M &= \max_{1\leq i\leq n} b_i \\
\end{eqnarray}
\bibliographystyle{acm}
\bibliography{paper}
\end{document}
\endinput

>>>>

\section{Steinberg's Algorithm}
\par In this section we introduce a more advanced approximation algorithm designed by \cite{steinberg1997strip}. Instead of heuristically packing every rectangle and output the height as result, Steinberg gave a more specific bound on the height $\hat{h}$ of the bin, with which a valid packing can be found easily. This is guaranteed by the following theorem.
\paragraph{Steinberg's Theorem} Suppose that $w_M=\max_{1\leq i\leq n}w_i$, $h_M=\max_{1\leq i\leq n}h_i$, $a_i=w_ih_i$, and $A=\sum_{i=1}^{n}$. If the following inequalities hold,
\begin{equation}
	w_M\leq w, h_M\leq h, 2A\leq wh-(2w_M-w)_+(2h_M-h)+
\end{equation}
then it is possible to pack the rectangles $R_1, R_2, \ldots, R_n$ into the rectangle $Q$ of size $w\times h$ by an efficient algorithm $M$\cite{steinberg1997strip}. The plus footnote returns the rectified linear value by $x_+=\max(x,0)$, which is a non-negative term.
\bibliographystyle{acm}
\bibliography{paper}
\end{document}
\endinput
